---
title: Hello, Quarto!
format: html
---

```{r}
#| include: false
library(tidyverse)
```

## Meet the cars
The [mtcars](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars) dataset contains fuel consumption and design characteristics for `{r} nrow(mtcars)` cars from the 1970s.

This dataset is built into R and is commonly used for teaching data analysis and visualization.

@fig-plot-mtcars shows the **relationship between a car’s weight and its fuel efficiency**.

```{r}
#| label: fig-plot-mtcars
#| fig-cap: Fuel efficiency vs weight for cars in the mtcars dataset
#| echo: false
ggplot(mtcars, 
       aes(x = wt, y = mpg)) +
  geom_point(aes(color = factor(cyl)), size = 2) +
  labs(
    x = "Weight (1000 lbs)",
    y = "Miles per gallon",
    color = "Number of cylinders"
  ) +
  theme_minimal()
```

## Compute Pearson Correlation
We compute the Pearson correlation coefficient between vehicle weight (wt) and fuel efficiency (mpg) to quantify the linear relationship shown in the plot. Pearson's $r$ ranges from $-1$ to $1$; a negative value indicates heavier cars tend to have lower mpg. The computed value helps assess the strength and direction of this association.

```{r}
cor_mpg_wt <- cor(mtcars$wt, mtcars$mpg, method = "pearson")
cor_mpg_wt
```